\documentclass{article}

\usepackage{array}
\usepackage{enumitem}
\usepackage[letterpaper, portrait, top=1.0in, right=0.5in, left=0.5in, bottom=1.5in]{geometry}
\usepackage[colorlinks=true, linkcolor=linkColor, urlcolor=linkColor, citecolor=linkColor, anchorcolor=linkColor]{hyperref}
\usepackage{multirow}
\usepackage{titlesec}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{fancyhdr}
\usepackage{fontspec}
\setmonofont{Hack Nerd Font}

\definecolor{blue}{HTML}{2079C7}
\definecolor{gray}{HTML}{666666}
\definecolor{linkColor}{HTML}{0000FF}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\pagenumbering{gobble}

\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\setlength{\headheight}{69pt}
\setlist[itemize]{noitemsep, leftmargin=1em}

\titleformat{\section}
    {\color{blue}\normalfont\Large\bfseries}
    {\color{blue}\thesection}{1em}{\large\uppercase}
\titleformat{\subsection}
    {\normalfont\Large\bfseries}
    {\thesection}{1em}{\normalsize}
\titleformat{\subsubsection}
    {\color{gray}\normalfont\Large\bfseries}
    {\color{gray}\thesection}{1em}{\small}

\titlespacing*{\section}
    {0em}{0em}{0em}
\titlespacing*{\subsection}
    {0em}{1em}{0em}
\titlespacing*{\subsubsection}
    {0em}{0em}{0em}

\begin{document}

\noindent

\pagestyle{fancy}
\fancyhead[L]{
	\begin{tabular}{L{.4\textwidth} l l}
		\multirow{2}{*}{\Huge{\textbf{Alejandro Angulo} }} & \small{\texttt{}} \space \href{https://github.com/alejandro-angulo}{https://github.com/alejandro-angulo} & \small{\texttt{󰖟}} \space \href{https://alejandr0angul0.dev}{https://alejandr0angul0.dev} \\
		                                                   & {\small{\texttt{}} \space \href{mailto:\email}\email}                                                    & \small{\texttt{}} \space \phonenumber                                                    \\ % chktex 1
	\end{tabular}
}
\fancyfoot[L]{
	The source code for this document is available at \href{https://github.com/alejandro-angulo/resume}{https://github.com/alejandro-angulo/resume}
}
\vspace*{-0.3in}
\hspace*{-2em}
\begin{minipage}[t]{.6\textwidth}
	\section*{Professional Experience}
	\subsection*{Sure  --- \textit{Staff Software Engineer}}
	\subsubsection*{February 2020--Present}
	\begin{itemize}
		\item Architected and led development of a configuration-driven platform
		      replacing bespoke per-client systems, enabling the full policy lifecycle
		      (quoting, binding, renewals, claims) to be managed through declarative
		      configuration; reduced partner onboarding from months to weeks.
		\item Led initiative to reduce configuration overhead by designing
		      replication infrastructure for environment-specific data, enabling
		      faster partner launches and reducing manual setup.
		\item Resolved critical database lock contention issue under load,
		      improving concurrent policy creation capacity from less than 20
		      to 150+ requests (previously caused application crashes) just in
		      time for partner marketing push.
		\item Discovered a multi-year critical vulnerability in authentication
		      service affecting all API endpoints that allowed arbitrary credential
		      generation; led immediate remediation effort and coordinated with
		      security team on long-term hardening strategy.
		\item Designed OpenAPI schema generation pipeline and auto-generated
		      TypeScript clients for frontend consumers, eliminating manual type maintenance
		      across teams.
		\item Served as primary incident responder, proactively monitoring
		      system health via Datadog and Sentry, rapidly diagnosing issues and
		      implementing fixes.
		\item Championed end-to-end testing in CI, driving cross-team adoption
		      and improving deployment confidence; mentored engineers on testing
		      practices and platform architecture through pairing and onboarding sessions.
	\end{itemize}
	\subsection*{Everbridge (formerly NC4) --- \textit{Software Engineer}}
	\subsubsection*{October 2018--February 2020}
	\begin{itemize}
		\item Developed and maintained Python (Django) and PHP applications
		      powering real-time alerting for emergency events (fires, police
		      activity, etc.).
		\item Led migration from SVN to Git, enabling modern code review
		      workflows and improving team collaboration.
		\item Re-architected monolithic Python application into modular
		      components, reducing coupling and simplifying onboarding for new
		      engineers.
		\item Established engineering standards including PEP8 compliance and
		      automated linting, improving code consistency across the team.
		\item Owned development of RESTful API for report generation, working
		      directly with product managers to balance technical debt with
		      feature delivery.
	\end{itemize}
	\subsection*{MedQIA --- \textit{Software Engineer}}
	\subsubsection*{April 2017--September 2018}
	\begin{itemize}
		\item Developed and maintained a Java desktop application used by
		      clinical readers and lab technologists to assist in clinical trials.
		\item Owned documentation and validation processes for FDA compliance,
		      ensuring audit readiness for regulated medical software.
		\item Built Python-based scan tracking system to monitor clinical trial
		      progress and surface actionable data to stakeholders.
		\item Extended Java application with Python plugin system, automating
		      clinical workflows (dynamic patient loading, task automation) for
		      end users.
	\end{itemize}
\end{minipage}
\hspace{0.08\textwidth}
\begin{minipage}[t]{.3\textwidth}
	\section*{About Me}
	Software engineer with a decade of experience building and scaling backend
	systems. I focus on designing maintainable architectures, improving developer
	experience, and helping engineers grow through mentorship and knowledge
	sharing. Currently pursuing an M.S. in Computer Science to formalize my
	computer science knowledge.
	\\
	\\
	Outside of my professional work, I like to tinker with computers. I've
	spent time building my own personal ``cloud'' (self-hosting things like my
	own git server, CI runner, storage, etc.). I've always been fascinated by
	tech and I'm eager to continue improving my skills and the skills of those
	around me.
	\vspace{1em}
	\section*{Toolset}
	Some tools/frameworks I use regularly in my current role:
	\begin{itemize}
		\item aws
		\item django
		\item docker
		\item git
		\item linux
		\item opencode (AI coding agent)
		\item postgresql
		\item python
		\item rabbitmq
		\item redis
		\item terraform
	\end{itemize}
	\section*{Education}
	\subsection*{Georgia Tech}
	\subsubsection*{M.S. in Computer Science}
	\subsubsection*{2026--Present}
	\subsection*{UC Davis}
	\subsubsection*{B.S. in Applied Physics}
	\subsubsection*{2012--2016}
\end{minipage}
\end{document}
